\subsection{Problem description}
There are multiple devices in the mobile market today, even though this allows every user to find a device of their choice this choice can become limited due to applications on their device not allowing their associates from other platforms to share their applications. This also limits organizations trying to provide applications since they need to decide which platform to launch it on.

To solve this problem we made an efficient backend service with modern technology that allows for many users of different devices to use at the same time, at the same time it should allow for expanding upon and reusing for different types of applications. A client application for the different platforms was made to provide both a showcase of the concept as well as finding out the differences between the platforms.


\subsection{Project delimitations}
For this project we decided the target application to be a game. The game should have a gameboard and questions to answer, for rules see Appendix 2. This type of application allows a clear way inside the application to see when other devices are changing the state of the application while also providing a usable end result. We choose to limit our target client devices to Android API v.19, iOS 7 as well as a web application for Chrome version 29. For the mobile devices it was decided that a single API should be used for the application to provide a similar experience between the platforms. The web application should bypass the API and use the services directly, this was decided to provide early testing of the services provided by the backend as well as a fully functional client.

